Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-17 PAPER/main.tex
added bullet points to comparison

@@

The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz. The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the number of strips $k$ in the optimal solution, which was calculated using Equation \ref{eqn:lowerbound}.

@@

>>>>

\begin{algorithm}
\caption{MFFD$^+$}
\label{alg:mffd+}
\begin{algorithmic}[1]
	\State Sort items in $\mathcal{I}$ in non-increasing order of widths $w_i$
	\For{$i \gets 1 \To |\mathcal{I}|$}	
		\State $j \gets 1$, packed $\gets \False$
		\While{\textbf{not} packed}
			\If{$S_j \in \mathcal{S}$ and $\sum_{i = 1}^{|S_j|}w_i + w_i \leq W$}
				\State Run AHC
				\If{AHC returns solution $\mathcal{F}$}
					\State $S_j \gets \mathcal{F}$
					\State packed $\gets \True$
				\Else \hspace{0.5mm} $j \gets j + 1$	
				\EndIf
			\ElsIf{$S_j \notin \mathcal{S}$}
				\State{$S_j \gets S_j \cup i$ in regular orientation}
				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
				\State packed $\gets \True$
			\EndIf
		\EndWhile
	\EndFor
	\Return $\mathcal{S}$
\end{algorithmic}	
\end{algorithm}

@@

The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz. The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.

@@

\begin{itemize}
	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve. Triplers are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
	\item Fair comparison, running over 1000 instances (average of 1000 instances)
	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
\end{itemize}
